---
title: "linear model from Web"
author: "Sierra Green"
date: "Fall 2021"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot
```{r}
boxplot(SIMS~ARM,data=data)
```


This model is kind of difficult to comprehend, however it seems that SIMS increases ARM by only a little.

### Numerical results
```{r}
cor(SIMS~ARM,data=data)
```

The average amount is 0.6860073. This is how much value is given to ARM.

### Inferential  (Build model.1)
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The p-value is 2.2e-16.

#### Predict at target point

We can barely tell the difference in SIMS~ARM because of how small the p-value. In this case I would reject the null hypothesis.


#### scatterplot with model fit
```{r}
boxplot(SIMS~ARM,data=data, SIMS~ARM + geom_point(aes(col=Sex)) + geom_smooth(method=lm))
```


## Model 2 SIM~GRIP

### Now add in scatterplot
```{r}
boxplot(SIMS~GRIP,data=data)
```


The Plot shows the GRIP increasing because of SIMS.

### Numerical results 
```{r}
cor(SIMS~GRIP,data=data)
```

The average amount is 0.6860073. This is how much value is given to GRIP.


### Inferential  (Build model.2)
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```  


The p-value is 2.2e.16.



#### predict model.2 at target point


The p-value is yet too small to tell the difference so therefore I will reject the null hypothesis.

#### now add the model fit to our plot for model.2
```{r}
boxplot(SIMS~GRIP,data=data,SIMS~GRIP + geom_point(aes(col=Sex)) + geom_smooth(method=lm))
```

boxplot(SIMS~GRIP,data=data,SIMS~GRIP + geom_point(aes(col=Sex)) + geom_smooth(method=lm)



## Model 3 SIM~ARM+GRIP


### Numerical results (cor)
```{r}
cor(SIMS~ARM+GRIP,data=data)
```

The average amount is 0.7326545. This is how much value is given to ARM and GRIP.

  
### Inferential  (Build 2-dimentional model.3)
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```



The p-value is 2.2e-16. It is very small which in this case the null hypothesis will be rejected.



#### predict model.3 at target point

I believe that model.3 is better than model.1 and model.2. Even though the p-value remains the same, the average results in 0.7326545.

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
```{r}
anova(model.1,model.3)
```


Model 1 is greater than model 3.


### Model.2 vs Model.3
```{r}
anova(model.2,model.3)
```



Model 2 is greater than model 3 in this comparison.



## Informally compare Model.1 with model.2
```{r}
anova(model.1,model.2)
```


The Res.Df for model 1 and model 2 are both 145, however SIMS-GRIP is better because of the RSS resulting in 243.07 rather than SIMS-ARM
resulting in 217.88.